Airy function: Kawai+Takei vs. Mari\~{n}o

### 2022-11-28 hypergeometric.tex

\begin{equation}\label{eq}
\big[P(\tfrac{\partial}{\partial z})+\tfrac{1}{z}Q(\tfrac{\partial}{\partial z})+\tfrac{1}{z}R(\tfrac{1}{z})\big]f(z)=0
\end{equation}
with $\deg P=2$, $\deg Q=1$ and $R=O(\tfrac{1}{z})$. We denote by $\alpha_1,\alpha_2$ the roots of $P(\lambda)$ and we assume they are distinct. Furthermore we assume $\tau_j:=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}\neq 0$. The latter assumption guarantees the formal solution $\tilde{f}$ being slight, while the former assumption implies there will be two independent solutions.

@@

>>>>

\begin{equation}\label{eq}
\big[P(\tfrac{\partial}{\partial z})+\tfrac{1}{z}Q(\tfrac{\partial}{\partial z})+\tfrac{1}{z}R(\tfrac{1}{z})\big]f(z)=0
\end{equation}
with $\deg P=2$, $\deg Q=1$ and $R=O(\tfrac{1}{z})$. We denote by $\alpha_1,\alpha_2$ the roots of $P(-\lambda)$ and we assume they are distinct. Furthermore we assume $\tau_j:=\frac{Q(\alpha_j)}{P'(\alpha_j)}\neq 0$. The latter assumption guarantees the formal solution $\tilde{f}$ being slight, while the former assumption implies there will be two independent solutions.

@@

\begin{prop}
We verify that 
\begin{equation}
\hat{f}(\zeta_1)=\left(1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)^{1-C} \, {}_2F_1\left(A-C+1,B-C+1;2-C;1-\frac{\zeta_1}{\alpha_2-\alpha_1} \right)
\end{equation}
\begin{equation}
\hat{f}(\zeta_2)=\left(1-\frac{\zeta_2}{\alpha_1-\alpha_2}\right)^{1-C} \, {}_2F_1\left(A-C+1,B-C+1;2-C;1-\frac{\zeta_2}{\alpha_1-\alpha_2} \right)
\end{equation}
are indeed resurgent.  
\end{prop}

\begin{proof}
\color{Tan}
Recall that the analytic continuation of Gauss hypergeometric functions is given in terms of other hypergeometric fucntions (see DLMF 15.2.3):
\begin{align*}
\hat{f}(\zeta_1+i0)-\hat{f}(\zeta_1-i0)&\propto\left(\frac{\zeta_1}{\alpha_1-\alpha_2}\right)^{C-A-B}\left(1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)^{1-C} {}_2F_1\left(1-A,1-B;C+1-A-B;\frac{\zeta_1}{\alpha_2-\alpha_1}\right)\\
&=(-1)^{C-A-B}\left(1-\frac{\zeta_2}{\alpha_1-\alpha_2}\right)^{C-A-B}\left(\frac{\zeta_2}{\alpha_1-\alpha_2}\right)^{1-C}\cdot\\
&\qquad\qquad \cdot {}_2F_1\left(1-A,1-B;C+1-A-B;1-\frac{\zeta_2}{\alpha_1-\alpha_2}\right)\\
\end{align*}
\color{black}
\end{proof}

\section{Hypergeometric functions as Borel transform of third order ODE}

Let us consider the following linear third order ODE

\begin{equation}\label{eq3}
\big[P(\tfrac{\partial}{\partial z})+\tfrac{1}{z}Q(\tfrac{\partial}{\partial z})+\tfrac{1}{z}R(\tfrac{1}{z})\big]f(z)=0
\end{equation}
with $\deg P=3$, $\deg Q=2$ and $R=O(\tfrac{1}{z})$. We denote by $\alpha_1,\alpha_2,\alpha_3$ the roots of $P(-\lambda)$ and we assume they are distinct. There are three possible scenarios illustrated in figure \ref{fig3} below:
\begin{itemize}
\item $|\alpha_1-\alpha_2|<|\alpha_2-\alpha_3|<|\alpha_1-\alpha_3|$
\item $|\alpha_2-\alpha_3|=|\alpha_1-\alpha_3|<|\alpha_1-\alpha_2|$
\item $|\alpha_1-\alpha_2|=|\alpha_2-\alpha_3|=|\alpha_1-\alpha_3|$
\end{itemize}

\begin{figure}[h]\label{fig3}
\begin{tikzpicture}
\draw [red](-1,1)--(-3,1);
\draw [green](-1,1)--(-1.25,3);
\draw [blue](-3,1)--(-1.25,3);
\node[font=\tiny, below] at (-3,1) {$\alpha_1$};
\node[font=\tiny, below] at (-1,1) {$\alpha_2$};
\node[font=\tiny, above] at (-1.25,3) {$\alpha_3$};
\draw [green](0.25,1)--(1.5,2);
\draw [red](0.25,1)--(2.75,1);
\draw [green](1.5,2)--(2.75,1);
\node[font=\tiny, below] at (0.25,1) {$\alpha_1$};
\node[font=\tiny, below] at (2.75,1) {$\alpha_2$};
\node[font=\tiny, above] at (1.5,2) {$\alpha_3$};
\draw [red](4,1)--(6,1);
\draw [red](4,1)--(5,2.73);
\draw [red](6,1)--(5,2.73);
\node[font=\tiny, below] at (4,1) {$\alpha_1$};
\node[font=\tiny, below] at (6,1) {$\alpha_2$};
\node[font=\tiny, above] at (5,2.73) {$\alpha_3$};
\end{tikzpicture}
\end{figure}

Furthermore we assume $\tau_j:=\frac{Q(\alpha_j)}{P'(\alpha_j)}\in\mathbb{Q}$. The latter assumption guarantees the formal solution $\tilde{f}$ being slight, while the former assumption implies there will be three independent solutions.

Under the previous assumptions we prove that the Borel transformed solution $\hat{f}(\zeta_j)$ is hypergeometric, $\zeta_j=\zeta-\alpha_j$.

\begin{prop}
Let $P(\lambda)=\lambda^3+a_2\lambda^2+a_1\lambda+a_0$, $Q(\lambda)=b_2\lambda^2+b_1\lambda+b_0$ and $R(\tfrac{1}{z})=\tfrac{c_1}{z}+\tfrac{c_2}{z^2}$ satisfying the previous assumptions. Then 
\begin{itemize}
\item if $|\alpha_1-\alpha_2|<|\alpha_2-\alpha_3|<|\alpha_1-\alpha_3|$
\color{red}
\begin{align}
\hat{f}(\zeta_1)&=\left(1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)^{c-1} \, {}_2F_1\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_1}{\alpha_2-\alpha_1} \right)\\
\hat{f}(\zeta_2)&=\left(1-\frac{\zeta_2}{\alpha_1-\alpha_2}\right)^{c-1} \, {}_2F_1\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_2}{\alpha_1-\alpha_2} \right)\\
\hat{f}(\zeta_3)&=\left(1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)^{c-1} \, {}_2F_1\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_3}{\alpha_2-\alpha_1} \right)
\end{align}
\color{black}
\item if $|\alpha_1-\alpha_2|<|\alpha_2-\alpha_3|=|\alpha_1-\alpha_3|$
\color{red}
\begin{align}
\hat{f}(\zeta_1)&=\left(1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)^{c-1} \, {}_2F_1\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_1}{\alpha_2-\alpha_1} \right)\\
\hat{f}(\zeta_2)&=\left(1-\frac{\zeta_2}{\alpha_1-\alpha_2}\right)^{c-1} \, {}_2F_1\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_2}{\alpha_1-\alpha_2} \right)\\
\hat{f}(\zeta_3)&=?
\end{align}
\color{black}
\item if $|\alpha_1-\alpha_2|=|\alpha_2-\alpha_3|=|\alpha_1-\alpha_3|$ 
\color{red}
\begin{align}
\hat{f}(\zeta_1)&=\left(1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)^{c-1} \, {}_3F_2\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_1}{\alpha_2-\alpha_1} \right)\\
\hat{f}(\zeta_2)&=\left(1-\frac{\zeta_2}{\alpha_1-\alpha_2}\right)^{c-1} \, {}_3F_2\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_2}{\alpha_1-\alpha_2} \right)\\
\hat{f}(\zeta_3)&=\left(1-\frac{\zeta_3}{\alpha_2-\alpha_1}\right)^{c-1} \, {}_3F_2\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_3}{\alpha_2-\alpha_1} \right)
\end{align}

\end{itemize}

\color{black}
where the coefficients $\mathbf{m}=(m_1,m_2,m_3),\mathbf{n}=(n_1,n_2)$ depend on the parameter of $P,Q,R$. 
\end{prop}

\begin{proof}
The strategy is analogous to the one for second order ODEs. Hence, we first consider the Borel transform of equation \ref{eq3}: 
\begin{multline}\label{borel 3}
P(-\zeta)\hat{f}+\int_0^\zeta Q(-\zeta')\hat{f}(\zeta')d\zeta'+c_1\int_0^\zeta(\zeta-\zeta')\hat{f}(\zeta')d\zeta'+\frac{c_2}{2}\int_0^\zeta(\zeta-\zeta')^2\hat{f}(\zeta')d\zeta'=0
\end{multline}

Although equation \eqref{borel 3} is an integral equation, since $\tilde{f}$ is slight, $\hat{f}$ is a solution of \eqref{borel 3} if and only if it is a solution of the third order ODE obtained by differentiating \eqref{borel 3} three times: 
\begin{multline}\label{borel_ODE 3}
\big[P(-\zeta)\partial_\zeta^3+(-3P'(-\zeta)+Q(-\zeta))\partial_\zeta^2+(3P''(-\zeta)-2Q'(-\zeta)+c_1)\partial_\zeta+(-P'''(-\zeta)+Q''(-\zeta)+c_2)\big]\hat{f}=0
\end{multline}

Notice that

\begin{align*}
P(-\zeta)&=(\zeta-\alpha_1)(\zeta-\alpha_2)(\zeta-\alpha_3)\\
-P'(-\zeta)&=(\zeta-\alpha_2)(\zeta-\alpha_3)+(\zeta-\alpha_1)(\zeta-\alpha_3)+(\zeta-\alpha_2)(\zeta-\alpha_1)\\
P''(-\zeta)&=6\zeta-2\alpha_1-2\alpha_2-2\alpha_3
\end{align*}

We now study separately the three scenarios:
\begin{itemize}
\item if $\ell=|\alpha_1-\alpha_2|<|\alpha_2-\alpha_3|<|\alpha_1-\alpha_3|$ we claim that \eqref{borel_ODE 3} is ??
\item if $\alpha_2=\alpha_3+\ell,\, \alpha_1=\alpha_3-\ell$ we claim that \eqref{borel_ODE 3} is a ??
\color{Aquamarine}
Change coordinates $y=\frac{\zeta-\alpha_1}{\ell}$:
\begin{align*}
P(-\zeta)\partial_\zeta^3&\longrightarrow -\ell^3y(\ell y+\alpha_1-\alpha_2)(\ell y+\alpha_1-\alpha_3)\frac{1}{\ell^3}\partial_y^3=y(1-y^2)\partial_y^3\\
(-3P'(-\zeta)+Q(-\zeta))\partial_\zeta^2&\longrightarrow (3\ell^{2}(3y^2-1)+Q(-\ell y-\alpha_1))\frac{1}{\ell^2}\partial_y^2\\
(3P''(-\zeta)-2Q'(-\zeta)+c_1)\partial_\zeta&\longrightarrow(-18\ell y-2Q'(-\ell y-\alpha_1)+c_1)\frac{1}{\ell}\partial_y\\
-P'''(-\zeta)+Q''(-\zeta)+c_2&\longrightarrow -6+2b_2+c_2
\end{align*}

Change coordinates $s=y^2$:
\begin{align*}
y(1-y^2)\partial_y^3&\longrightarrow 8(1-s)s^2\partial_s^3+12(1-s)s\partial_s^2\\
(3\ell^{2}(3y^2-1)+Q(-\ell y-\alpha_1))\frac{1}{\ell^2}\partial_y^2&\longrightarrow \big[6(3s-1)+2(b_2s+\frac{2b_2\alpha_1-b_1}{\ell}y+\frac{b_2\alpha_1^2-\alpha_1b_1+b_0}{\ell^2})\big](\partial_s+2s\partial_s^2)\\
(-18\ell y-2Q'(-\ell y-\alpha_1)+c_1)\frac{1}{\ell}\partial_y&\longrightarrow 4(2b_2-9)s\partial_s+2\frac{4b_2\alpha_1-2b_1+c_1}{\ell}y\partial_s
\end{align*}

\begin{multline}
\Big[8(1-s)s^2\partial_s^3+\big[4(6+b_2)s+4\frac{2b_2\alpha_1-b_1}{\ell}y+4\frac{b_2\alpha_1^2-\alpha_1b_1+b_0}{\ell^2}\big]s\partial_s^2\Big.\\
\Big.\big[-2(9-2b_2)s-2(3-2b_2)+2\frac{b_2\alpha_1^2-\alpha_1b_1+b_0}{\ell^2}+2\frac{6b_2\alpha_1-3b_1+c_1}{\ell}y\big]\partial_s-6+2b_2+c_2\Big]\hat{f}=0
\end{multline}

\begin{align*}
\frac{2b_2\alpha_1-b_1}{\ell}y+\frac{b_2\alpha_1^2-\alpha_1b_1+b_0}{\ell^2}=2n_1+2n_2-2\\
6+b_2=-2(3+m_1+m_2+m_3)\\
\big[-(3-2b_2)+2(\frac{b_2\alpha_1^2-\alpha_1b_1+b_0}{\ell^2})+\frac{8b_2\alpha_1-4b_1+c_1}{\ell}y\big]=4n_1n_2\\
(9-2b_2)=4(1+m_1+m_2+m_3+m_1m_2+m_1m_3+m_2m_3)\\
-6+2b_2+c_2=8m_1m_2m_3
\end{align*}
\color{black}
\item if $|\alpha_1-\alpha_2|=|\alpha_2-\alpha_3|=|\alpha_1-\alpha_3|=\ell$ we claim that \eqref{borel_ODE 3} is a generalized hypergeometric equation. Without loss of generality we assume $\alpha_2=\alpha_1+\ell$ and $\alpha_3=\alpha_1+\frac{\ell}{2}+i\frac{\sqrt{3}}{2}\ell$.

Change coordinates $y=\frac{\zeta-\alpha_1}{\ell}+\frac{\sqrt{3}+i}{2}$, then 
\begin{align*}
P(-\zeta)\partial_\zeta^3&\longrightarrow -\ell y(\ell y+\alpha_1-\alpha_2)(\ell y+\alpha_1-\alpha_3)\frac{1}{\ell^3}\partial_y^3=y(1-y^2)\partial_y^3\\
(-3P'(-\zeta)+Q(-\zeta))\partial_\zeta^2&\longrightarrow (3\ell^{2}(3y^2-1)+Q(-\ell y-\alpha_1))\frac{1}{\ell^2}\partial_y^2\\
(3P''(-\zeta)-2Q'(-\zeta)+c_1)\partial_\zeta&\longrightarrow(-18\ell y-2Q'(-\ell y-\alpha_1)+c_1)\frac{1}{\ell}\partial_y\\
-P'''(-\zeta)+Q''(-\zeta)+c_2&\longrightarrow -6+2b_2+c_2
\end{align*} 
\end{itemize}

### 2022-11-28 kawai+takei vs mariño.tex

\usepackage{ajf}
\usepackage{amsthm}

\theoremstyle{definition}
\newtheorem{defn}{Definition}
\theoremstyle{plain}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}

\DeclareMathOperator{\Ai}{Ai}

@@

With $w = x \eta^{2/3}$, the equation above is equivalent to
\[ \left[\left(\frac{d}{dw}\right)^2 - w \right] \psi(w \eta^{-2/3}, \eta) = 0. \]
Proof: substitute back to get
\begin{align*}
\left[\eta^{-4/3} \left(\frac{d}{dx}\right)^2 - \eta^{2/3} x \right] \psi(x, \eta) = 0 \\
\left[\eta^{-4/3} \left(\frac{d}{dx}\right)^2 - \eta^{-4/3} \eta^2 x \right] \psi(x, \eta) = 0 \\
\eta^{-4/3} \left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0.
\end{align*}
Hence, $\psi(w \eta^{-2/3}, \eta) = k(\eta) \Ai(w)$ is a solution for any holomorphic function $k$.

>>>>

%\usepackage{ajf}
\usepackage{amsthm}

\theoremstyle{definition}
\newtheorem{defn}{Definition}
\theoremstyle{plain}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{xcolor}
%\DeclareMathOperator{\Ai}{Ai}

@@

With $w = x \eta^{2/3}$, the equation above is equivalent to
\[ \left[\left(\frac{d}{dw}\right)^2 - w \right] \psi(w \eta^{-2/3}, \eta) = 0. \]
Proof: substitute back to get
\begin{align*}
\left[\eta^{-4/3} \left(\frac{d}{dx}\right)^2 - \eta^{2/3} x\right] \psi(x, \eta) = 0 \\
\left[\eta^{-4/3} \left(\frac{d}{dx}\right)^2 - \eta^{-4/3}\eta^2 x \right] \psi(x, \eta) = 0 \\
\eta^{-4/3} \left[\left(\frac{d}{dx}\right)^2 - \eta^2 x\right] \psi(x, \eta) = 0.
\end{align*}
Hence, $\psi(w \eta^{-2/3}, \eta) = k(\eta) \mathsf{Ai}(w)$ is a solution for any holomorphic function $k$.

\section{Veronica's change of coordinates}

Kawai and Takei study the WKB analysis of the equation

\begin{equation}
\label{WKB_Airy} 
\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0 
\end{equation}
as $\eta\to\infty$. They define $\psi_B(x, y)$ as the inverse Laplace transform of $\psi(x, \eta)$ with respect to $\eta$. In the coordinates $t=yx^{-3/2}$ they find an explicit formula for $\psi_B(x,y)$ in terms of Gauss hypergeometric functions:
\begin{align*}
\psi_{+,B}(x,y)&=\frac{1}{x}\phi_+(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}s^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};s\right)\\
\psi_{-,B}(x,y)&=\frac{1}{x}\phi_-(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}(1-s)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};1-s\right)
\end{align*}
where $s=3t/4+1/2$. 
The same hypergeometric functions have been computed in Section ?? as the Borel transform of the formal solutions of the Airy equation

\begin{equation}
\label{Airy}
\left[\left(\frac{d}{dw}\right)^2 -  w \right] f(w) = 0.
\end{equation}

Although the two equations look closely related (they are equivalent by the change of coordinates $w=x\eta^{2/3}$), the Borel transform of $\psi$ is computed with respect to $\eta x^{3/2}$ (which is the conjugate variable of $t$) while the Borel transform of $f(w)$ is computed with respect to $w$. So we need to find a different change of coordinates to explain why the Borel transforms of $\psi(x,\eta)$ and $f(w)$ are given by the same hypergeometric function.

First of all notice that if $\eta$ and $y$ are conjugate variables under Borel transform, meaning 
\begin{align*}
\sum_{n\geq 0}a_n\eta^{-n-1}  \overset{\mathcal{B}}{\longrightarrow} \sum_{n\geq 0}\frac{a_n}{n!} y^{n} 
\end{align*} 
then $t=yx^{-3/2}$ is the conjugate variable of $q=\eta x^{3/2}$ up to correction by a factor of $x^{-3/2}$
\begin{align*}
\sum_{n\geq 0}a_nq^{-n-1}=\sum_{n\geq 0}a_nx^{-3/2(n+1)}\eta^{-n-1}  \overset{\mathcal{B}}{\longrightarrow} \sum_{n\geq 0}\frac{a_nx^{-3/2(n+1)}}{n!} y^{n}=x^{-3/2}\sum_{n\geq 0}\frac{a_n}{n!} t^{n}. 
\end{align*}
In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$. Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}, then $\Phi(q)$ solves 
\begin{equation}
\label{eq_Phi}
\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2} - \eta^2 x \right] \Phi(q) = 0
\end{equation}

\begin{proof}
\begin{align*}
&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0\\
&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] x^{1/2}\Phi(q) = 0\\
&\frac{d}{dx}\left[\frac{1}{2}x^{-1/2}\Phi+x^{1/2}\frac{d}{dx}\Phi\right]-\eta^2x^{3/2}\Phi=0\\
&-\frac{1}{4}x^{-3/2}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+x^{1/2}\left(\frac{d}{dx}\right)^2\Phi-\eta^2x^{3/2}\Phi=0\\
&\left[x^{1/2}\left(\frac{d}{dx}\right)^2+x^{-1/2}\frac{d}{dx}-\frac{1}{4}x^{-3/2}-\eta^2x^{3/2}\right]\Phi=0\\
&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0
\end{align*}
\end{proof}
Now rewrite \eqref{eq_Phi} in the coordinates $q=\eta x^{3/2}$: 
\begin{align*}
&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
&\left[\frac{9}{4}\eta^2x\left(\frac{d}{dq}\right)^2+\frac{3}{4}\eta x^{-1/2}\frac{d}{dq}+x^{-1}\cdot\frac{3}{2}\, \eta\,  x^{1/2}\frac{d}{dq}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
&\left[\eta^2x\left(\frac{d}{dq}\right)^2+\frac{1}{3}\eta x^{-1/2}\frac{d}{dq}+\frac{2}{3}\, \eta\,  x^{-1/2}\frac{d}{dq}-\frac{1}{9}x^{-2}-\frac{4}{9}\eta^2x\right]\Phi=0\\
&\left[\eta^2\left(\frac{d}{dq}\right)^2+\eta x^{-3/2}\frac{d}{dq}-\frac{1}{9}x^{-3}-\frac{4}{9}\eta^2\right]\Phi=0\\
&\left[\left(\frac{d}{dq}\right)^2+\eta^{-1} x^{-3/2}\frac{d}{dq}-\frac{1}{9}\eta^{-2}x^{-3}-\frac{4}{9}\right]\Phi=0\\
&\left[\left(\frac{d}{dq}\right)^2+q^{-1}\frac{d}{dq}-\frac{1}{9}q^{-2}-\frac{4}{9}\right]\Phi=0
\end{align*}

therefore $\Phi(q)$ is a solution of the transform Airy equation (see draft2).
